### 2021-06-10 paper/appendix_data.tex

\subsection{Contacts by age}

As mentioned in section \ref{sec:matching}, the probability that two individuals are
matched can depend on background characteristics. In particular, we allow this
probability to depend on age and county of residence. While we do not have good data on
geographical assortativity and just roughly calibrate it such that 80\% of contacts are
within the same county, we can calibrate the assortative mixing by age from the same
data we use to calibrate the number of contacts.

>>>>

\subsection{Contacts by age}
\label{subsec:contacts_by_age}

As mentioned in section \ref{sec:matching}, the probability that two individuals are
matched can depend on background characteristics. In particular, we allow this
probability to depend on age and county of residence. While we do not have good data on
geographical assortativity and just roughly calibrate it such that 80\% of contacts are
within the same county, we can calibrate the assortative mixing by age from the same
data we use to calibrate the number of contacts.\comment[id=HM]{Redo
\ref{fig:assortativity_other} /\ref{fig:assortativity_work} with total number of
contacts or better add a similar figure showing total number of contacts by age in all
networks}

### 2021-06-10 paper/report.tex

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations or rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections, the final level is always the
highest in case the vaccination campaign had been running in isolation (red lines). The
Shapley value decomposition shows that vaccinations contribute about
15\%\comment[id=HM]{check!} to the cumulative difference between scenarios. Reasons for
this are the slow start---it took until 24~March until 10\% of the population had
received their first vaccination, the 20\% mark was reached on April 19th ---and the
focus on older individuals. These groups contribute less to the spread of the disease
than others due to a lower number of contacts, see~\ref{fig:assortativity}. It is
important to note that the initial focus of the campaign was to prevent deaths and
severe disease; the case fatality was rate considerably lower during the third wave when
compared to the second (4.4\% between October and February and 1.4\% between March and
June). It is important to note that by the end of our study period, when first-dose
vaccination rates reached around 40\% of the population, the numbers of new cases would
have started to decline.

@@

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached around mid-May and it would be June for the comparison with the seasonality-only
scenario. The effect on total cases, however, is visible immediately. Despite the fact
that only a small fraction of the population performed weekly rapid tests in
March\footnote{X\% in the model; 27\% of respondents to the COSMO study reported in
    early March that they \textit{ever} did a rapid test)}\comment[id=HM]{Put in}, new
infections on April 1 would be reduced by 53\% relative to the scenario without
vaccinations, rapid tests, or seasonality.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the
three channels for rapid tests. Tests for pupils have the smallest effect, which is
largely explained by the relatively small number of students (XXM vs. YYM workers) and
the fact that schools did not operate at full capacity during our period of study.
Almost 40\% come from tests at the workplace. Despite the fact that we phase rapid tests
for private reasons are phased in only late, they make up for more than half of the total effect.

@@

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operaton was not back until the beginning of
June. In light of the large negative effects school closures have on children and
parents\comment[id=HM]{need to cite a couple of poor learning outcomes / mental health
papers. There must be well-published ones}---and in particular on those with low
socio-economic status---

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
        \caption{{Effects of different schooling scenarios after Easter}}
        \label{fig:schooling_scenarios_easter}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/new_work_scenarios/full_newly_infected}
        \caption{{Effects of different work scenarios after Easter}}
        \label{fig:to_be_determined}
    \end{subfigure}
    \vskip3ex

    \caption{Effects of different scenarios for schooling and working from home}
    \label{fig:interventions_school}

    \floatfoot{\noindent Note: All aggregates; See S.XXX for statistics by age group and
        by geographical region.}

>>>>

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations or rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections with only one channel active,
the final level is always the highest in case of the vaccination campaign (orange
lines). The Shapley value decomposition shows that vaccinations contribute about 15\% to
the cumulative difference between scenarios. Reasons for this are the slow start---it
took until March~24th until 10\% of the population had received their first vaccination,
the 20\% mark was reached on April 19th---and the focus on older individuals. These
groups contribute less to the spread of the disease than others due to a lower number of
contacts, see Supplementary Material~\ref{subsec:contacts_by_age}. It is important to
note that the initial focus of the campaign was to prevent deaths and severe disease;
the case fatality was rate considerably lower during the third wave when compared to the
second (4.4\% between October and February and 1.4\% between March and June). It is
important to note that by the end of our study period, when first-dose vaccination rates
reached around 40\% of the population, the numbers of new cases would have started to
decline.

@@

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known, which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached around mid-May and it would be June for the comparison with the seasonality-only
scenario. The effect on total cases, however, is visible immediately. Despite the fact
that only a small fraction of the population performed weekly rapid tests in
March\footnote{X\% in the model; 27\% of respondents to the COSMO study reported in
    early March that they \textit{ever} did a rapid test)}\comment[id=HM]{Put in}, new
infections on April 1 would be reduced by 53\% relative to the scenario without
vaccinations, rapid tests, or seasonality.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the
three channels for rapid tests. Tests for pupils have the smallest effect, which is
largely explained by the relatively small number of students (XXM pupils vs. YYM
workers)\comment[id=HM]{fill in} and the fact that schools did not operate at full
capacity during our period of study. Almost 40\% come from tests at the workplace.
Despite the fact that we phase rapid tests for private reasons are phased in only late,
they make up for more than half of the total effect.

@@

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operaton was not back until the beginning of
June. Figure~\ref{fig:school_scenarios} shows the effects of different policies regarding school starting at Easter, a point where rapid tests had become widely available.

In light of the large negative effects school closures have on children and
parents\comment[id=HM]{need to cite a couple of poor learning outcomes / mental health
papers. There must be well-published ones}---and in particular on those with low
socio-economic status---the results in

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/school_scenarios/full_newly_infected}
        \caption{{Effects of different schooling scenarios}}
        \label{fig:school_scenarios}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/new_work_scenarios/full_newly_infected}
        \caption{{Effects of different work scenarios}}
        \label{fig:workplace_scenarios}
    \end{subfigure}
    \vskip3ex

    \caption{Effects of different scenarios for policies regarding schools and workplaces.}
    \label{fig:school_workplace_scenarios}

    \floatfoot{\noindent Note: Interventions start at Easter because there were no
        capacity constraints for rapid tests afterwards.}
